\textbf{Computational Fuzzy Extractors}

### 2013-02-19 CompFuzzExtUnp.tex
Working on impossibility of verifiable and unpredictable sketches

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\textbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}

@@

\begin{lemma}
Let $X$ be the uniform distribution over $\zo^b$.  Suppose that $(\sketch, \rec)$ is a $(\zo^b, b, r, t)$ unpredictable sketch for $\epsilon = 0, s_{sec} = \Omega(|\rec|)$ with error $\delta$.  Then $r < b - t -\log (1-\delta)$.
\end{lemma}
\begin{proof}
It suffices to show that $H^{\unp}_{0, s_{sec}}( X | \sketch(X)) < b-t + \log (1-\delta)$.  That is, it suffices to construct $D$ such that $\Pr[D(\sketch(X)) = X] > 2^{-b+t} (1-\delta)$.  We describe $D$:
\begin{enumerate}
\item Input $s = \sketch(x)$.
\item Sample $z \leftarrow \zo^b$.
\item Output $\rec(z, s)$.
\end{enumerate}
Now 
\[
\Pr[D(\sketch(X)) = X] \geq \Pr[Z \in B_t(X)] \Pr[\rec(Z, \sketch(X)) =X | \dis(Z, X)\leq t] = 2^{-b+t}(1-\delta)
\]
That is $r < b-t-\log (1-\delta)$.
\end{proof}
\bnote{Note we are underestimating the probability that $z\in B_t(x)$.  Just don't want to find the right probability right now.}
\end{document}

>>>>

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\ver}{\ensuremath{\class{Ver}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\textbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}

@@

\begin{lemma}
\label{lem:impossibility of sketch with eps = 0}
Let $X$ be the uniform distribution over $\zo^b$.  Suppose that $(\sketch, \rec)$ is a $(\zo^b, b, r, t)$ unpredictable sketch for $\epsilon = 0, s_{sec} = \Omega(|\rec|)$ with error $\delta$.  Then $r < b - t -\log (1-\delta)$.
\end{lemma}
\begin{proof}
It suffices to show that $H^{\unp}_{0, s_{sec}}( X | \sketch(X)) < b-t + \log (1-\delta)$.  That is, it suffices to construct $P$ such that $\Pr[P(\sketch(X)) = X] > 2^{-b+t} (1-\delta)$.  We describe $P$:
\begin{enumerate}
\item Input $s = \sketch(x)$.
\item Sample $z \leftarrow \zo^b$.
\item Output $\rec(z, s)$.
\end{enumerate}
Now 
\[
\Pr[P(\sketch(X)) = X] \geq \Pr[Z \in B_t(X)] \Pr[\rec(Z, \sketch(X)) =X | \dis(Z, X)\leq t] = 2^{-b+t}(1-\delta)
\]
That is $r < b-t-\log (1-\delta)$.
\end{proof}
\bnote{Note we are underestimating the probability that $z\in B_t(x)$.  Just don't want to find the right probability right now.}

We will now consider the impossibility result where $\epsilon \neq 0$.  We will focus on the case where $\rec$ is verifiable, that is, given an $x, s = \sketch(y)$ it is possible to tell whether $x$ is the value encoded in $s$.

\begin{definition}
We say a sketch $(\sketch, \rec)$ is $\delta$-verifiable if there exists an efficient randomized function $\ver$ such that with probability $1-\delta$ over the coins of $\sketch, \ver$ for all $y$ in the domain of $\sketch$, $\ver(y', \sketch(y)) = 1$ implies that $y=y'$.  That is, 
\[
\forall y\in \mathcal{M}, \Pr[\exists y'\neq y \wedge \ver(y', \sketch(y)) = 1]\leq \delta
\]
Furthermore, $\forall y\in\mathcal{M}, \Pr[\ver(y, \sketch(y)) = 1] =1$.
\end{definition}

We now show that if a sketch is unpredictable then either the quality or quantity of the unpredictability entropy must depend on $t$.
\begin{theorem}
Let $W$ be the uniform distribution over $\zo^b$.  Suppose that $(\sketch, \rec)$ is a $(\zo^b, b, r, t)$ unpredictable sketch that is $\delta$-verifiable with verifier $\ver$.   Furthermore assume that $(\sketch, \rec)$ is  $\epsilon, \Omega(|\rec|+|\ver|)$-secure.  Then $r<b-t -\log (1-\epsilon - \delta)$.  That is, either $r$ or $\epsilon$ depends on $t$.
\end{theorem}
\begin{proof}
Let $(\sketch, \rec)$ be a $\delta$-verifiable secure sketch with verification function $\ver$.  Let $W$ be the source, then we have the following claim:
\begin{claim}
If $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W))) \leq \epsilon$ for $s_{sec} = \Omega(|\ver|)$ then $\Pr[W = Y]\geq 1-\epsilon - \delta$.
\end{claim}
\begin{proof}
We define a distinguisher $D(x, s) = \ver (x, s)$.  Then note that, 
\begin{align*}
1-\epsilon &\leq \Pr[D(Y, \sketch(W)) =1] = \Pr[\ver(Y, \sketch(W)) = 1] \\
&\leq \Pr[\ver(Y, \sketch(W)) = 1 | \ver\text{ is unique}]\Pr[\ver\text{ is unique}] \\&+ \Pr[\ver(Y, \sketch(W)) = 1 | \ver\text{ is not unique}]\Pr[\ver\text{ is not unique}]\\
&\leq \Pr[Y = W | \sketch(W)]\Pr[\ver \text{ is unique}] +\Pr[\ver\text{ is not unique}]\\
&\leq \Pr[Y= W | \sketch(W)](1-\delta) + \delta
\end{align*}
This means that $\Pr[Y | \sketch(W)=W | \sketch(W)]\geq \frac{(1-\epsilon -\delta)}{(1-\delta)}\geq 1-\epsilon -\delta$.
\end{proof}
Thus, since $W = Y$ with high probability, any predictor for $W$ is also a predictor for $Y$.  We reuse the predictor from \lemref{lem:impossibility of sketch with eps = 0}.  Define $P$ as above.  Then 
\[
\Pr[P(\sketch(W) )= Y] \geq \Pr[P(\sketch(W) )= W]\Pr[W = Y | \sketch(W)]\geq 2^{-b+t}(1-\epsilon-\delta)
\]
If $\epsilon$ does not depend on $t$ then the remaining entropy must depend on $t$.  The statement of theorem follows.
\end{proof}
\end{document}
